Artin Group Presentations Arising from Cluster Algebras

### 2014-07-20 Paper.tex
minor abstract adjustments

\begin{abstract}
In 2003, Fomin and Zelevinsky proved that finite-type cluster algebras can be classified by Dynkin diagrams. Then in 2013, Barot and Marsh defined the presentation of a reflection group associated to a Dynkin diagram in terms of an edge-weighted, oriented graph, and proved that this group is invariant (up to isomorphism) under diagram mutations. In this paper, we extend Barot and Marsh's results to Artin group presentations, defining new relations for when the generators are not self-inverses and again showing mutation-invariance for these presentations.
\end{abstract}

>>>>

\begin{abstract}
In 2003, Fomin and Zelevinsky proved that finite-type cluster algebras can be classified by Dynkin diagrams. Then in 2013, Barot and Marsh defined the presentation of a reflection group associated to a Dynkin diagram in terms of an edge-weighted, oriented graph, and proved that this group is invariant (up to isomorphism) under diagram mutations. In this paper, we extend Barot and Marsh's results to Artin group presentations, defining new generator relations and showing mutation-invariance for these presentations.
\end{abstract}
